\pagestyle{empty}
\begin{center}
\textup{\large{\textbf{ABSTRACT}}}
\end{center}

\justify
\indent
The Book Cataloguing System is an application for maintaining a person's books-be it physical copies or e-books. In this project I tried to show the working of an online book catalogue and cover the basic functionality of the same. To develop a project for solving the organisational issues of a user when it comes to large number of books; in order to nurture the needs of an end user by providing various ways to choose the most suitable book. Also to enable the users to have additional functionalities which are inclusive of physical book copies.


The Book Cataloguing System undertaken as a project is based on relevant technologies. The main aim of this project is to develop software for that makes the management of books easier for an end user. This project has been developed to carry out the processes easily and quickly, which is not possible with a manual system.


The project analyzes the system requirements and then comes up with the requirements specifications. It studies other related systems and then come up with system specifications. The system is then designed in accordance with specifications to satisfy the requirements. The system design is then implemented with SQLite, CSHARP. The system is designed as an interactive content management system. The content management system deals with DML operations and validation while the interactive system deals with system interaction with the users.


This mini project has been implemented using CSHARP to design the interface and SQLite at the backend.


\pagebreak
