\chapter{DESCRIPTION OF TOOLS AND TECHNOLOGIES}
\section{Microsoft visual Studio}
Microsoft Visual Studio is an integrated development environment(IDE) from Microsoft. It is used to develop console and graphical user interface applications along with Windows Form applications, websites, web applications, and web services in both native code together with managed code for all platforms supported by Microsoft Window, Windows Mobile, Windows CE, .NET Framework, .NET Compact Framework and Microsoft Silverlight. Microsoft Visual Studio simplifies the basic tasks of creating, debugging and deploying applications.
Microsoft Visual Studio comes with .NET Framework and supports applications targeting Windows. It supports IBM DB2 and Oracle databases, in addition to Microsoft SQL Server. It has integrated support for developing Microsoft Silverlight applications, including an interactive designer. Microsoft Visual Studio offers several tools to make parallel programming simpler: in addition to the Parallel Extensions for the .NET Framework and the Parallel Patterns Library for native code, Visual Studio includes fools for debugging parallel applications.
The Visual Studio code editor now highlights references; whenever a symbol is selected; all other usages of the symbol are highlighted. It also offers a Quick Search feature to incrementally search across all symbols in C++, Csharp and VB.NET projects. Quick Search supports substring matches and camel Case searches. The Call Hierarchy feature allows the developers to see all the methods that are called from a current method as well as the methods that call the current one. IntelliSense in Visual Studio supports a consume-first mode which developers can opt into. In this mode, IntelliSense will not auto-complete identifiers; this allows the developer to use undefined identifiers (like variable or method names) and define those later. Visual Studio can also help in this by automatically defining them, if it can infer their types from usage.
We have used Visual Studio Community 2015, v 14.0.23107.10 for developing the Inventory Management System Application.

\section{Microsoft SQL server Management Studio Express}
Microsoft SQL Server Management Studio Express (SSMSE) provides a graphical management tool for SQL Server Express Edition. SSMSE user interface is a subset of SQL Management Studio that is available with other editions of SQL Server. SSMSE call also manage instance of the SQL Server Database Engine created by any edition of SQL Server. Inventory Management System is developed using Microsoft SOL Server 2008.
\section{NET Framework 4.5}
The .NET Framework is a development platform for building apps for Windows, Windows Phone, Windows Server, and Microsoft Azure. It consists of the common language runtime (CLR) and the .NET Framework class library, which includes classes, interfaces, and value types that support an extensive range of technologies. The .NET Framework provides a managed execution environment, simplified development and deployment, and integration with a variety of programming languages, including Visual Basic and Visual Cshrap.
\section{.NET Framework Structure}
The .Net architecture is basically segregated in to three layers namely top, middle and bottom layer. The bottom layer is CLR, it is the heart of .NET Framework which provides the runtime environment in which programs are executed. The middle layer comprises the next generation of standard system services are brought under the control of the framework, making them universally available and standardizing their usage across languages.
\section{The .NET Language}
In the past, you chose the development language for an application based upon the functionality that you were trying to perform. Some languages were more powerful than others, but at the same time they might have required a higher level of understanding and were, in most cases, more difficult to program in.Now the .NET Framework provides you with a language-independent programming platform. You do not have to decide which language would provide a better solution. All languages are now on a level playing field. In .NET, no one language is superior to any of the other languages. They all have equal access to everything that .NET offers.
To be part of the .NET Framework, a language only has to follow certain rules. The biggest and most important rule for inclusion is that the language needs to be an object-oriented language. Microsoft provides four languages with the .NET Framework:
Visual Basic .NET
Csharp
C++.NET and
Jscript .NET.
Microsoft also provides Jsharp (pronounced J-sharp), but in order to use this new language that is basically Java for .NET, you need to download the language to install it on your server.
Data Provider:
The data provider is responsible for providing and maintaining the connection to the database. A database provider is a set of related components that works together to provide in an efficient and performance driven manner. Each Data provider consists of the following components classes:
 The command object which is used to execute a command.
 The Connection object which provides a connection to the database.
 The Data Reader object which provides a ready only, connects recordset.
\section{The Connection object}
The connection object created the connection to the database. Microsoft Visual Studio .NET provides two types of connection classes: the SQLconnection object, which is designed specifically to connect to Microsoft SQL Server.
\section{The command Object}
The command object is represented by corresponding classes: SQL Command. Command object are used to execute commands to a database across a data connection. The command objects provides three methods that are used to execute commands on the database.
19
 ExecuteNonQuery: Executes commands that have no return values such as INSERT, UPDATE AND DELETE
 ExecuteScalar: Returns a single value from a database query
 ExecuteReader: Returns a result set by way of a DataReader Objects.
\section{The Data Reader object}
The DataReadre object provides a read-only, connected stream recordset from a database. Unlike other components of the Data Provider, DataReader objects cannot be directly instantiated. Rather, the DateReader is returned as the result of the Command objectsExecute Reader method. The DataReader can provide rows of data directly to application logic when one does not need to keep the data cached in memory. Because only one row is in memory in time, the DateReader provides the lowest overhead in terms of system performance but requires the exclusive use of an open Connection object for the life time of the DataReader.
\section{Microsoft SQL Server}
Microsoft SQL Server is an application used to create computer databases for the Microsoft Windows family of server operating systems. Microsoft SQL Server provides an environment used to generate database that can be accessed from workstations, the Internet, or other media such as a personal digital assistant (PDA). Microsoft SQL Server is used to create desktop, enterprise, and web-based database applications. It is used at different levels and with various goals.
SQL Server makes simpler and easier to deploy, manage, and optimize enterprise data and analytical applications. An enterprise data management platform, it performs a single management console that enables data administrators anywhere in your organization to monitor, manage, and tune all of the databases and associated services across your enterprise. It provides an extensible management infrastructure that can be easily programmed by using SQL management objects, enabling users to customize and extend their management environment and independent software vendors to build additional tools and functionality to further extend the capabilities that come out of the box.
SQL Server simplifies management by providing integrated management console to monitor and manage the SQL Server relational database as well as integration services, analysis services, reporting services, notification services and SQL Server Mobile Edition across large number of distributed servers and databases. Databaseadministrator can perform several tasks at the same time, such as authorizing and executing a query, viewing server objects, managing an object, monitoring system activities, and viewing online help.
SQL Server expose more than 70 new measures of internal database performance and resource usages, ranging from memory, locking, and scheduling to transactions and network and disk I/O. these dynamic management views provide greater transparency and visibility into the database and a powerful infrastructure for proactive monitoring of database health and performance. The major characteristics are listed below:
Reliability: achieve a more secure deployment. SQL Server provides rich security features to protect data and network resources.
Confidentiality: Protect your data. SQL Server clustering supports Kerberos authentication on a virtual Server and Microsoft-style policies on standard logins so that a consistent policy is applied across all accounts in the domain.
Integrity: SQL Server supports encryption capabilities within database itself, fully integrated with a key management infrastructure. By default, client server communications are in encrypted.administrator can perform several tasks at the same time, such as authorizing and executing a query, viewing server objects, managing an object, monitoring system activities, and viewing online help.
SQL Server expose more than 70 new measures of internal database performance and resource usages, ranging from memory, locking, and scheduling to transactions and network and disk I/O. these dynamic management views provide greater transparency and visibility into the database and a powerful infrastructure for proactive monitoring of database health and performance. The major characteristics are listed below:
Reliability: achieve a more secure deployment. SQL Server provides rich security features to protect data and network resources.
Confidentiality: Protect your data. SQL Server clustering supports Kerberos authentication on a virtual Server and Microsoft-style policies on standard logins so that a consistent policy is applied across all accounts in the domain.
Integrity: SQL Server supports encryption capabilities within database itself, fully integrated with a key management infrastructure. By default, client server communications are in encrypted.
